; AlifePlus barter policy. NPC-to-NPC item swap, no money (the counterpart of ap_trade_policy.ltx,
; which is the visiting stalker vs a service trader with cash). One uniform block, no rank tiers, same
; shape as ap_stash_policy.ltx and ap_loot_policy.ltx. DLTX-overridable.
;
; Same category system as trade: keys are engine-derived (xinventory.get_category / get_category_opts
; resolves ammo_slot_2/3_tN per the NPC's equipped pistol/rifle, ammo_not_equipped, grenades,
; medical/food/drink). Each row is a category band in the HOLDER's perspective: min = keep at least
; this many, max = give away above this. An item moves from A to B when A holds it above A's max
; (surplus) AND B holds it below B's min (deficit). Ammo counts in rounds; items otherwise. Total
; items moved per barter event is capped by MCM barter_max_items (economy > barter).
;
; Weapons, outfits, and helmets are NOT count-band rows here -- the barter orchestrator handles them on
; a separate cost-upgrade pass (a spare moves only when its get_cost beats the receiver's equipped one),
; so they are absent from this block. Untouchable and equipped items are dropped by
; xinventory.get_category before any policy lookup.

[ap_barter_policy]
ammo_slot_3_t1    = 15, 45
ammo_slot_2_t1    = 16, 48
ammo_slot_3_t2    = 15, 45
ammo_slot_2_t2    = 16, 48
ammo_not_equipped = 0, 0
grenade_f1        = 1, 3
grenade_rgd5      = 1, 3
grenade_gd-05     = 1, 3
grenade_ammo      = 0, 0
medkit            = 1, 3
bandage           = 1, 4
stim              = 0, 2
antirad           = 1, 2
pill              = 0, 3
food              = 1, 2
drink             = 1, 2
artefact          = 0, 0
device            = 0, 0
crafting          = 0, 3
other             = 0, 0
