; AlifePlus loot policy. Single uniform block. DLTX-overridable.
; Applied by ap_ext_loot_select to what an NPC just looted from a corpse: for each capped key,
; the cheapest looted members are deleted until the NPC's whole-inventory count for that key is at
; or under max, so the kept loot is the highest-value. Only this pickup is trimmed; the standing
; loadout is left to the AlifeBalance cull (whose ceilings match these GATHER caps).
;
; Row shape: `key = min, max`. Loot uses MAX only (min is ignored -- a pickup is never "filled"
; to a minimum). A key is a category name or a single item section name. A key left unlisted is
; never trimmed; money is the only intentional case. Combat ammo is capped at the 3-box CAP
; (45 rifle / 48 pistol; box_size 15 / 16) so an NPC can scavenge spare boxes but not hoard up
; to the cull ceiling. grenade_smoke = 0 drops looted smoke on pickup (engine crash when NPCs
; throw it). Untouchable (quest / anim / blacklisted) and equipped items are skipped
; automatically by the xinventory categorizer regardless of policy contents.

[ap_loot_policy]
ammo_slot_3_t1    = 0, 45
ammo_slot_3_t2    = 0, 45
ammo_slot_2_t1    = 0, 48
ammo_slot_2_t2    = 0, 48
ammo_not_equipped = 0, 0
grenade           = 0, 3
grenade_smoke     = 0, 0
grenade_ammo      = 0, 3
medkit            = 0, 5
bandage           = 0, 5
antirad           = 0, 3
stim              = 0, 3
pill              = 0, 3
food              = 0, 5
drink             = 0, 3
weapon            = 0, 1
outfit            = 0, 1
helmet            = 0, 1
artefact          = 0, 3
device            = 0, 1
crafting          = 0, 3
other             = 0, 3
