; AlifePlus faction market policy, all rows in the TRADER's perspective (the counterpart file,
; ap_trade_policy.ltx, is the visiting stalker's perspective). Two directions, one filter chain:
; [ap_market_trader_buy] echoes what the faction's traders bought from stalkers onto the shelf at
; restock, rank-gated and priced at a premium; [ap_market_trader_sell] removes a share of what
; those traders sold to stalkers from the freshly respawned shelf at the same restock.
; DLTX-overridable. Categories are engine-derived (xinventory.get_section_category over Parse_ITM
; _ITM buckets + curated consumable sets); nothing here invents sections.
;
; [ap_market_trader_buy] specials (single numeric values, not category rows):
;   fifo_max            distinct sections kept per faction (bounded dedup FIFO, oldest evicted;
;                       one depth for both the bought and the sold FIFO)
; Price premium and spawn condition are MCM settings (Economy > Faction market), not here.
; Category/section rows: key = per-trader cap (max copies of that key at one trader).
;   A key is a category (medkit, device, ...) or a single item section. An item uses its
;   section rule when listed, else its category rule; a key absent here is NEVER injected.
;   Cap 0 = listed-but-excluded (same as absent for injection). Ammo counts in rounds.

[ap_market_trader_buy]
fifo_max            = 20

artefact            = 1
device              = 2
medkit              = 3
bandage             = 3
antirad             = 2
stim                = 2
food                = 3
drink               = 3
grenade             = 2
; grenade_smoke is bugged; cap 0 keeps the market from ever echoing it while the grenade category
; is otherwise sold (cap 0 = listed-but-excluded, same rejection as absent).
grenade_smoke       = 0

; Weapons and armor are injection-capable but left off. To enable, uncomment a row (value = max copies per trader):
;weapon             = 1
;outfit             = 1
;helmet             = 1

; Trader-sell whitelist: which keys the sell-out may remove from a trader's fresh stock, value =
; max sections of that key removed per restock (same row shape and filter chain as injection,
; own scope). The sell-out mirrors what the faction's stalkers actually buy (ap_trade_policy),
; so only the staples they consume are listed: ammo and medical supplies. A key absent here is
; NEVER removed. ammo_not_equipped is the context-free ammo category every ammo section resolves
; to. The removal share per section is the MCM trader sell-out slider (Economy > Faction market).
[ap_market_trader_sell]
ammo_not_equipped   = 4
medkit              = 3
bandage             = 3
stim                = 2

; Hard rank floor: a category (or single section) here is blocked until the player reaches the
; named rank tier. Tier names per game_relations.ltx [game_relations] rating
; (novice/trainee/experienced/professional/veteran/expert/master/legend).
[ap_market_rank_floor]
artefact = veteran

; Per-rank cost band: for the player's current tier, the first "cost:chance" whose cost >= the
; item cost wins (ascending). Cheap items stay common at low rank; expensive items rare at low
; rank. A tier with no row falls back to [default]; a cost above every threshold takes the last
; (rarest) entry.
[ap_market_rank_chance]
novice       = 3000:1.0, 12000:0.30, 999999:0.05
trainee      = 5000:1.0, 18000:0.40, 999999:0.10
experienced  = 8000:1.0, 25000:0.50, 999999:0.15
professional = 12000:1.0, 35000:0.60, 999999:0.25
veteran      = 20000:1.0, 999999:0.50
expert       = 30000:1.0, 999999:0.70
master       = 999999:1.0
legend       = 999999:1.0
default      = 8000:1.0, 25000:0.50, 999999:0.15
