; AlifePlus overlay on top of vanilla gulag_job_trade_buy_sell.ltx.
; Read by ap_ext_trade.get_keep_items() (allowlist), ap_ext_trade.get_rank_gated_items()
; (veteran+ restriction), and ap_ext_trade._buy_phase() (restock targets).
;   1. `[ap_buy_sell_keep]`: AP-namespaced allowlist of items NPCs treat as useful.
;      Drives BOTH sell-skip (NPC keeps these) and buy-include (NPC restocks these).
;   2. `[ap_buy_sell_veteran]`: rank-gated buy list. NPCs only buy these sections if their
;      character rank is veteran or higher (>= RANK_VETERAN = 12000). Applies to any
;      buy-phase section -- keep-list items (grenades) AND ammo classes inferred from the
;      equipped pistol/rifle (premium variants: AP, EP, hot-load, hollow-point, steel-core,
;      flechette, intermediate +damage rounds). FMJ baseline and single-tier ammo stay
;      unlisted so all ranks restock them. Sell-skip protection is rank-independent.
;   3. Restock flips on vanilla `[buy_sell_supplier]` / `[buy_sell_medic]` rows whose
;      restock=0 blocks the buy phase from acting on them despite their membership in
;      the allowlist (grenades, AI medkits).

@[ap_buy_sell_keep]
device_pda        = 1
device_pda_1      = 1
device_pda_2      = 1
device_pda_3      = 1
bandage           = 1
medkit            = 1
medkit_army       = 1
medkit_scientic   = 1
stimpack          = 1
stimpack_army     = 1
stimpack_scientic = 1
tetanus           = 1
yadylin           = 1
analgetic         = 1
medkit_ai1        = 1
medkit_ai2        = 1
medkit_ai3        = 1
grenade_f1        = 1
grenade_rgd5      = 1

@[ap_buy_sell_veteran]
grenade_f1           = 1
grenade_rgd5         = 1
ammo_9x18_pmm        = 1
ammo_9x18_ap         = 1
ammo_9x19_pbp        = 1
ammo_9x19_ap         = 1
ammo_5.7x28_ss190    = 1
ammo_7.62x25_ps      = 1
ammo_11.43x23_hydro  = 1
ammo_5.45x39_ep      = 1
ammo_5.45x39_ap      = 1
ammo_5.56x45_ss190   = 1
ammo_5.56x45_ap      = 1
ammo_9x39_ap         = 1
ammo_7.62x39_ap      = 1
ammo_7.92x33_ap      = 1
ammo_7.62x51_ap      = 1
ammo_7.62x54_7h14    = 1
ammo_7.62x54_ap      = 1
ammo_12.7x55_ap      = 1
ammo_12x76_dart      = 1

![buy_sell_supplier]
grenade_f1   = 2,3,1,0.5,2
grenade_rgd5 = 2,3,1,0.5,2

![buy_sell_medic]
medkit_ai1 = 1,1,1,0.5,1
medkit_ai2 = 1,1,1,0.5,1
medkit_ai3 = 1,1,1,0.5,1
